%-------------------------
% Resume in Latex
% Author : Aryan Pathania
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aryan Pathania} \\ \vspace{1pt}
    \small +81 070 9099 5020 $|$ \href{mailto:aryan.pathania2003@gmail.com}{\underline{aryan.pathania2003@gmail.com}}
    $|$ Tokyo, Japan
    \\ \vspace{1pt}
    
    \href{https://linkedin.com/in/aynp}{\underline{linkedin.com/in/aynp}} $|$
    \href{https://github.com/aynp}{\underline{github.com/aynp}} $|$
    \href{https://codeforces.com/profile/sad_hamster_meme}{\underline{codeforces.com/profile/sad\_hamster\_meme}} $|$
    \href{https://aynp.dev/}{\underline{aynp.dev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology}{Hamirpur}
      {Bachelor of Technology in Computer Science and Engineering}{Dec. 2020 -- May 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Mercari}{Feb 2025 -- Present}
      {Backend Developer (Go)}{Roppongi, Tokyo, Japan}
    \resumeItemListStart
  \resumeItem{Owned notification delivery services processing \textbf{300M+ messages/day} across push, in-app, email, and LINE.}
  \resumeItem{Migrated LINE notification delivery from a third-party platform (Braze) to an in-house CRM, owning the end-to-end rollout and operating the system at \textbf{20M+ notifications/day}.}
\resumeItem{Enhanced a segmentation system enabling \textbf{attribute-based querying and filtering} over large user datasets, supporting targeted notification delivery at scale.}
  % \resumeItem{Enabled campaign-level \textbf{notification tracking} by propagating event semantics across delivery and client logging.}
  \resumeItem{Enabled campaign-level \textbf{notification tracking} by propagating event semantics across delivery and client logging, supporting \textbf{experimentation and analysis}.}
  \resumeItem{Enabled \textbf{international rollout of notification delivery} by implementing region-based configuration and templates, coordinating with client teams for incident-free launch in Hong Kong and Taiwan.}
  \resumeItem{Built an internal assistant end-to-end that provides real-time answers to marketer queries by \textbf{securely orchestrating BigQuery access} within internal tooling.}
\resumeItemListEnd

    \resumeSubheading
      {Flipkart}{Sep 2024 -- Jan 2025}
      {SDE 1 (Scala)}{Bengaluru, India}
\resumeItemListStart
  \resumeItem{Built backend data processing systems in the User Insights (Top of Funnel) team to support personalization and discovery features used by \textbf{200M+ annual active users}.}
  \resumeItem{Developed production data pipelines supplying features for \textbf{content search and retrieval} models at scale.}
  \resumeItem{Maintained backend API handlers for evolving upstream schemas; resolved production issues.}
\resumeItemListEnd

    \resumeSubheading
      {True Beacon}{Feb 2024 -- Sep 2024}
      {SDE (Go, Python)}{Bengaluru, India}
\resumeItemListStart
\resumeItem{Re-architected a large Spark ETL pipeline using Prefect and Polars by redesigning data flows and in-memory transformations, \textbf{reducing runtime from 10 hours to 6 minutes} and significantly lowering compute costs.}
  \resumeItem{Implemented unified observability for backend services using OpenTelemetry, enabling end-to-end tracing and faster production issue resolution.}
  \resumeItem{Deployed an internal API gateway to manage secure inter-service communication across backend services.}
  \resumeItem{Built internal automation tools and data pipelines to collect and process market and accounting data, and enhanced dashboards used by finance teams.}
\resumeItemListEnd

    \resumeSubheading
      {Mercari}{May 2023 -- Aug 2023}
      {Backend Developer Intern (Go)}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Resolved message queue backpressure causing multi-hour delays in coupon distribution, improving reliability of promotional delivery pipelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Other Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Open Source} $|$ \emph{Go, Lua, Docker, Kubernetes}}{}
      \resumeItemListStart
        \resumeItem{\textbf{Apache APISIX} – Extended the Ingress Controller by enhancing Kubernetes routing and security CRDs to support advanced request matching and conditional mTLS behavior.}
        \resumeItem{\textbf{ArgoCD} – Fixed cross-platform path resolution issues for environments without a standard \texttt{HOME} variable.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Data Structures and Algorithms}}{}
      \resumeItemListStart
        \resumeItem{Strong foundations in data structures and algorithms, applied through consistent problem-solving practice.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, C++, JavaScript, TypeScript} \\
     \textbf{Frameworks}{: Express, Next, gRPC } \\
     \textbf{Tools and Platforms}{: Git, Docker, Kubernetes, GitHub Actions, Apache Kafka, Google Cloud Platform (GCP)} \\
     % \textbf{Platforms}{: Google Cloud Platform (GCP), Amazon Web Services (AWS)} \\
     \textbf{Databases}{: Google Cloud Spanner, Postgres, Redis, BigQuery }
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
